---
title: Append ID to AMA (Boston) Event Data
output: html_document
---

This data analysis is to label the member in the AMA (Boston) Even data with their AMA membership
ID using the AMA membership files from Sep 2013 to Dec 2016 (missing Aug 2015 data).

This file needs to set the current working directory to where it contains the two folders. To run this file, instead of press the "Knit HTML" button in R Studio, type "rmarkdown::render("AMA_Boston_ID.Rmd")" in the console. This will knit in the current session instead of a background session, so that you can play with the varialbes in console. This pdf file will be updated, but you have to click open it.


```{ r setup}
opts_chunk$set(echo = TRUE, tidy = TRUE)
```

```{r results = "hide"}
library(xlsx);
library(dplyr);
setwd("C:/Clients/2016 AMA Boston/XiWang");
filePath1 <- c("/Original_membership_data/");
filePath2 <- c("/Boston_Event_Data/");
```
## 1. Read in Event data.
```{r ReadInBosEvt, cache = TRUE}
 BosEvt <- read.xlsx(paste(getwd(),filePath2,"AMABostonEvent.xlsx",sep = ""), sheetIndex = 1);
```

## 2. Read in Membership data.
```{r ReadInSep2013, cache = TRUE}
Sep2013<- read.xlsx(paste(getwd(),filePath1,"2013 09_September AMA Membership.xlsx",sep = ""), sheetIndex = 1);
```

```{r ReadInOct2013,cache = TRUE}
Oct2013<- read.xlsx(paste(getwd(),filePath1,"2013 10_October AMA Membership.xlsx",sep = ""), sheetIndex = 1);
```

```{r ReadInNov2013, cache = TRUE}
Nov2013<- read.xlsx(paste(getwd(),filePath1,"2013 11_November AMA Membership.xlsx",sep = ""), sheetIndex = 1);
```

```{r ReadInDec2013,cache=TRUE}
Dec2013<-read.xlsx(paste(getwd(),filePath1, "2013 12_December AMA Membership.xlsx",sep=""), sheetIndex = 1);
```

```{r ReadInJan2014,cache=TRUE}
Jan2014<-read.xlsx(paste(getwd(),filePath1, "2014 01_January AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInFeb2014,cache=TRUE}
Feb2014<-read.xlsx(paste(getwd(),filePath1,"2014 02_February AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInMar2014,cache=TRUE}
Mar2014<-read.xlsx(paste(getwd(),filePath1,"2014 03_March AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInApr2014,cache=TRUE}
Apr2014<-read.xlsx(paste(getwd(),filePath1,"2014 04_April AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInMay2014,cache=TRUE}
May2014<-read.xlsx(paste(getwd(),filePath1,"2014 05_May AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInJun2014,cache=TRUE}
Jun2014<-read.xlsx(paste(getwd(),filePath1,"2014 06_June AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInJul2014,cache=TRUE}
Jul2014<-read.xlsx(paste(getwd(),filePath1,"2014 07_July AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInAug2014,cache=TRUE}
Aug2014<-read.xlsx(paste(getwd(),filePath1,"2014 08_August AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInSep2014,cache=TRUE}
Sep2014<-read.xlsx(paste(getwd(),filePath1,"2014 09_September AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInOct2014,cache=TRUE}
Oct2014<-read.xlsx(paste(getwd(),filePath1,"2014 10_October AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInNov2014,cache=TRUE}
Nov2014<-read.xlsx(paste(getwd(),filePath1,"2014 11_November AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInDec2014,cache=TRUE}
Dec2014<-read.xlsx(paste(getwd(),filePath1,"2014 12_December AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInJan2015,cache=TRUE}
Jan2015<-read.xlsx(paste(getwd(),filePath1,"2015 01_January AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInFeb2015,cache=TRUE}
Feb2015<-read.xlsx(paste(getwd(),filePath1,"2015 02_February AMA Membership.xlsx",sep=""), sheetIndex = 1);
```

```{r ReadInMar2015,cache=TRUE}
Mar2015<-read.xlsx(paste(getwd(),filePath1,"2015 03_March AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInApr2015,cache=TRUE}
Apr2015<-read.xlsx(paste(getwd(),filePath1,"2015 04_April AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInMay2015,cache=TRUE}
May2015<-read.xlsx(paste(getwd(),filePath1,"2015 05_May AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInJun2015,cache=TRUE}
Jun2015<-read.xlsx(paste(getwd(),filePath1,"2015 06_June AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInJul2015,cache=TRUE}
Jul2015<-read.xlsx(paste(getwd(),filePath1,"2015 07_July AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInSep2015,cache=TRUE}
Sep2015<-read.xlsx(paste(getwd(),filePath1,"2015 09_September AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInOct2015,cache=TRUE}
Oct2015<-read.xlsx(paste(getwd(),filePath1,"2015 10_October AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInNov2015,cache=TRUE}
Nov2015<-read.xlsx(paste(getwd(),filePath1,"2015 11_November AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInDec2015,cache=TRUE}
Dec2015<-read.xlsx(paste(getwd(),filePath1,"2015 12_December AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInJan2016,cache=TRUE}
Jan2016<-read.xlsx(paste(getwd(),filePath1,"2016 01_January AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInFeb2016,cache=TRUE}
Feb2016<-read.xlsx(paste(getwd(),filePath1,"2016 02_February AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInMar2016,cache=TRUE}
Mar2016<-read.xlsx(paste(getwd(),filePath1,"2016 03_March AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInApr2016,cache=TRUE}
Apr2016<-read.xlsx(paste(getwd(),filePath1,"2016 04_April AMA Membership.xlsx",sep=""), sheetIndex = 1);
```

```{r ReadInMay2016,cache=TRUE}
May2016<-read.xlsx(paste(getwd(),filePath1,"2016 05_May AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInJun2016,cache=TRUE}
Jun2016<-read.xlsx(paste(getwd(),filePath1,"2016 06_June AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInJul2016,cache=TRUE}
Jul2016<-read.xlsx(paste(getwd(),filePath1,"2016 07_July AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInAug2016,cache=TRUE}
Aug2016<-read.xlsx(paste(getwd(),filePath1,"2016 08_August AMA Membership.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInSep2016,cache=TRUE}
Sep2016<-read.xlsx(paste(getwd(),filePath1,"2016 09_September AMA Membership.xlsx",sep=""), sheetIndex = 1);
```

```{r ReadInOct2016,cache=TRUE}
Oct2016<-read.xlsx(paste(getwd(),filePath1,"MemberRoster_10 October 2016.xlsx",sep=""), sheetIndex = 1);
```

```{r ReadInNov2016,cache=TRUE}
Nov2016<-read.xlsx(paste(getwd(),filePath1,"MemberRoster_11 November 2016.xlsx",sep=""), sheetIndex = 1);
```

```{r ReadInDec2016,cache=TRUE}
Dec2016<-read.xlsx(paste(getwd(),filePath1,"MemberRoster_12 December 2016.xlsx",sep=""), sheetIndex = 1);
```

## 3. Convert membership file ID, names, email, address.
```{r convertIDNameEamilAddress}
# Nov2013 is not included in NAMES.
NAMES<-c("Sep2013","Oct2013","Dec2013","Jan2014","Feb2014","Mar2014",
          "Apr2014","May2014","Jun2014","Jul2014","Aug2014","Sep2014",
          "Oct2014","Nov2014","Dec2014","Jan2015","Feb2015","Mar2015",
          "Apr2015","May2015","Jun2015","Jul2015","Sep2015","Oct2015",
          "Nov2015","Dec2015","Jan2016","Feb2016","Mar2016","Apr2016",
          "May2016","Jun2016","Jul2016","Aug2016","Sep2016","Oct2016",
          "Nov2016","Dec2016");

for (i in NAMES)
{j = get(i);
j$MEMBER.ID <- as.numeric(paste(j$MEMBER.ID));

j$FIRST.NAME[j$FIRST.NAME == "" | j$FIRST.NAME == " "] <- NA;
j$FIRST.NAME <- tolower(as.character(j$FIRST.NAME));

j$MIDDLE.NAME[j$MIDDLE.NAME == "" | j$MIDDLE.NAME == " "] <- NA;
j$MIDDLE.NAME <- tolower(as.character(j$MIDDLE.NAME));

j$LAST.NAME[j$LAST.NAME == "" | j$LAST.NAME == " "] <- NA;
j$LAST.NAME <- tolower(as.character(j$LAST.NAME));

j$LABEL.NAME[j$LABEL.NAME == "" | j$LABEL.NAME == " "] <- NA;
j$LABEL.NAME <- tolower(as.character(j$LABEL.NAME));

j$EMAIL.ADDRESS[j$EMAIL.ADDRESS == "" | j$EMAIL.ADDRESS == " "] <- NA;
j$EMAIL.ADDRESS <- tolower(as.character(j$EMAIL.ADDRESS));

j$COMPANY.NAME[j$COMPANY.NAME == "" | j$COMPANY.NAME == " "] <- NA;
j$COMPANY.NAME <- tolower(as.character(j$COMPANY.NAME));

j$PRIMARY.ADDRESS.1[j$PRIMARY.ADDRESS.1 == "" | j$PRIMARY.ADDRESS.1 == " "] <- NA;
j$PRIMARY.ADDRESS.1 <- tolower(as.character(j$PRIMARY.ADDRESS.1));

j$PRIMARY.ADDRESS.2[j$PRIMARY.ADDRESS.2 == "" | j$PRIMARY.ADDRESS.2 == " "] <- NA;
j$PRIMARY.ADDRESS.2 <- tolower(as.character(j$PRIMARY.ADDRESS.2));

j$SECONDARY.ADDRESS.1[j$SECONDARY.ADDRESS.1 == "" | j$SECONDARY.ADDRESS.1 == " "] <- NA;
j$SECONDARY.ADDRESS.1 <- tolower(as.character(j$SECONDARY.ADDRESS.1));

j$SECONDARY.ADDRESS.2[j$SECONDARY.ADDRESS.2 == "" | j$SECONDARY.ADDRESS.2 == " "] <- NA;
j$SECONDARY.ADDRESS.2 <- tolower(as.character(j$SECONDARY.ADDRESS.2));

j$PRIMARY.CITY[j$PRIMARY.CITY == "" | j$PRIMARY.CITY == " "] <- NA;
j$PRIMARY.CITY <- tolower(as.character(j$PRIMARY.CITY));

j$PRIMARY.STATE[j$PRIMARY.STATE == "" | j$PRIMARY.STATE == " "] <- NA;
j$PRIMARY.STATE <- tolower(as.character(j$PRIMARY.STATE));

j$PRIMARY.POSTAL.CODE[j$PRIMARY.POSTAL.CODE == "" | j$PRIMARY.POSTAL.CODE == " "] <- NA;

j$PRIMARY.COUNTRY[j$PRIMARY.COUNTRY == "" | j$PRIMARY.COUNTRY == " "] <- NA;
j$PRIMARY.COUNTRY <- tolower(as.character(j$PRIMARY.COUNTRY));

assign(i,j);
}
```

## 4. Convert the date to date type.
```{r convertDate,results="hide"}
# These are the files with date format: "%Y-%m-%d"
NAMES3 <-c("Sep2013","Oct2014","Nov2014","Dec2014","Jan2015","Feb2015",
           "Mar2015","Apr2015","May2015","Jun2015","Jul2015","Sep2015",
           "Oct2015","Nov2015","Dec2015","Jan2016","Feb2016","Mar2016",
           "Apr2016","May2016","Jun2016","Jul2016","Aug2016","Sep2016",
           "Oct2016","Nov2016","Dec2016");

# These are the files with date format: "%m/%d/%Y"
NAMES4<-c("Oct2013","Dec2013","Jan2014","Feb2014","Mar2014","Apr2014",
          "May2014","Jun2014","Jul2014","Aug2014","Sep2014");

# MEMBER.SINCE.DATE
for (i in NAMES3)
{j = get(i);
j$MEMBER.SINCE.DATE <- as.Date(j$MEMBER.SINCE.DATE,"%Y-%m-%d");
assign(i,j);
}

for (i in NAMES4)
{j = get(i);
j$MEMBER.SINCE.DATE <- as.Date(j$MEMBER.SINCE.DATE,"%m/%d/%Y");
assign(i,j);
}

# EXPIRATION.DATE
for (i in NAMES3)
{j = get(i);
j$EXPIRATION.DATE <- as.Date(j$EXPIRATION.DATE,"%Y-%m-%d");
assign(i,j);
}

for (i in NAMES4)
{j = get(i);
j$EXPIRATION.DATE <- as.Date(j$EXPIRATION.DATE,"%m/%d/%Y");
assign(i,j);
}

# DATE.PULLED
for (i in NAMES3)
{j = get(i);
j$DATE.PULLED <- as.Date(j$DATE.PULLED,"%Y-%m-%d");
assign(i,j);
}

for (i in NAMES4)
{j = get(i);
j$DATE.PULLED <- as.Date(j$DATE.PULLED,"%m/%d/%Y");
assign(i,j);
}


# NAMES5 are the ones that these four columns need to be converted 
# to date type:"ADDRESS.CHANGE.DATE", "COMMUNICATION.CHANGE.DATE",
# "STUDENT.GRADUATION.DATE", "DATE.LAST.MODIFIED".
# It turns out that NAMES5 is the same as NAMES4
NAMES5 <-c("Oct2013","Dec2013","Jan2014","Feb2014","Mar2014",
           "Apr2014","May2014","Jun2014","Jul2014","Aug2014","Sep2014");

# ADDRESS.CHANGE.DATE
for (i in NAMES5)
{j = get(i);
j$ADDRESS.CHANGE.DATE <- as.Date(j$ADDRESS.CHANGE.DATE,"%m/%d/%Y");
assign(i,j);
}

# COMMUNICATION.CHANGE.DATE
for (i in NAMES5)
{j = get(i);
j$COMMUNICATION.CHANGE.DATE <- as.Date(j$COMMUNICATION.CHANGE.DATE,"%m/%d/%Y");
assign(i,j);
}

# NAMES6 are the ones whose COMMUNICATION.CHANGE.DATE are logic type.
NAMES6 <-c("May2015","Jun2015","Jul2015","Sep2015","Oct2015",
           "Dec2015","Jan2016","Mar2016","Apr2016","May2016","Jul2016",
           "Aug2016");

# COMMUNICATION.CHANGE.DATE
for (i in NAMES6)
{j = get(i);
j$COMMUNICATION.CHANGE.DATE <- as.Date(as.character(j$COMMUNICATION.CHANGE.DATE),"%m/%d/%Y");
assign(i,j);
}


# STUDENT.GRADUATE.DATE
for (i in NAMES5)
{j = get(i);
j$STUDENT.GRADUATION.DATE <- as.Date(j$STUDENT.GRADUATION.DATE,"%m/%d/%Y");
assign(i,j);
}

# DATE.LAST.MODIFIED
for (i in NAMES5)
{j = get(i);
j$DATE.LAST.MODIFIED <- as.Date(j$DATE.LAST.MODIFIED,"%m/%d/%Y");
assign(i,j);
}
```

## 5. Merge all the membership files (except Nov2013).
```{r mergeAllMemberFiles}
identical(Sep2015$COMPANY.NAME,Sep2015$COMPANY.NAME.1);
Sep2015<-subset(Sep2015,select= (names(Sep2015) != "COMPANY.NAME.1"));

All<-Sep2013;
for (i in NAMES[2:length(NAMES)])
{j = get(i);
All<-merge(All,j,all=TRUE); 
}

dim(All);

# double chekc if All has any NA values.
dim(All[is.na(All$MEMBER.ID),]);
dim(All[is.na(All$MEMBER.SINCE.DATE),]);
dim(All[is.na(All$EXPIRATION.DATE),]);
dim(All[is.na(All$DATE.PULLED),]);
dim(All[is.na(All$STATUS),]);
dim(All[is.na(All$FIRST.NAME),]);
dim(All[is.na(All$LAST.NAME),]);
dim(All[is.na(All$EMAIL.ADDRESS),]);
```

## 6. Include the Nov2013 data.
```{r MergeNov2013}
Nov2013$MEMBER.ID  <- as.numeric(paste(Nov2013$MEMBER.ID));

Nov2013$FIRST.NAME[Nov2013$FIRST.NAME == "" | Nov2013$FIRST.NAME == " "] <- NA;
Nov2013$FIRST.NAME <- tolower(as.character(Nov2013$FIRST.NAME));

Nov2013$MIDDLE.NAME[Nov2013$MIDDLE.NAME == "" | Nov2013$MIDDLE.NAME == " "] <- NA;
Nov2013$MIDDLE.NAME <- tolower(as.character(Nov2013$MIDDLE.NAME));

Nov2013$LAST.NAME[Nov2013$LAST.NAME == "" | Nov2013$LAST.NAME == " "] <- NA;
Nov2013$LAST.NAME <- tolower(as.character(Nov2013$LAST.NAME));

Nov2013$COMPANY.NAME[Nov2013$COMPANY.NAME == "" | Nov2013$COMPANY.NAME == " "] <- NA;
Nov2013$COMPANY.NAME <- tolower(as.character(Nov2013$COMPANY.NAME));

Nov2013$PRIMARY.CITY[Nov2013$PRIMARY.CITY == "" | Nov2013$PRIMARY.CITY == " "] <- NA;
Nov2013$PRIMARY.CITY <- tolower(as.character(Nov2013$PRIMARY.CITY));

Nov2013$PRIMARY.STATE[Nov2013$PRIMARY.STATE == "" | Nov2013$PRIMARY.STATE == " "] <- NA;
Nov2013$PRIMARY.STATE <- tolower(as.character(Nov2013$PRIMARY.STATE));

Nov2013$PRIMARY.POSTAL.CODE[Nov2013$PRIMARY.POSTAL.CODE == "" | Nov2013$PRIMARY.POSTAL.CODE == " "] <- NA;

Nov2013$PRIMARY.COUNTRY[Nov2013$PRIMARY.COUNTRY == "" | Nov2013$PRIMARY.COUNTRY == " "] <- NA;
Nov2013$PRIMARY.COUNTRY <- tolower(as.character(Nov2013$PRIMARY.COUNTRY));

Nov2013$PRIMARY.ADDRESS.1[Nov2013$PRIMARY.ADDRESS.1 == "" | Nov2013$PRIMARY.ADDRESS.1 == " "] <- NA;
Nov2013$PRIMARY.ADDRESS.1 <- tolower(as.character(Nov2013$PRIMARY.ADDRESS.1));

Nov2013$PRIMARY.ADDRESS.2[Nov2013$PRIMARY.ADDRESS.2 == "" | Nov2013$PRIMARY.ADDRESS.2 == " "] <- NA;
Nov2013$PRIMARY.ADDRESS.2 <- tolower(as.character(Nov2013$PRIMARY.ADDRESS.2));


Nov2013$DATE.PULLED <- as.Date("2013-11-30",format = "%Y-%m-%d");
All <- merge(All, Nov2013, all = TRUE);
```
## 7. Convert name, email, company, address in event data.
```{r BosEvt}
BosEvt$First.Name <- tolower(as.character(BosEvt$First.Name));
BosEvt$Last.Name <- tolower(as.character(BosEvt$Last.Name));
BosEvt$Email <- tolower(as.character(BosEvt$Email));

BosEvt$Home.Address.1[BosEvt$Home.Address.1 == "" | BosEvt$Home.Address.1 == " "] <- NA;
BosEvt$Home.Address.1 <- tolower(as.character(BosEvt$Home.Address.1));

BosEvt$Home.Address.2[BosEvt$Home.Address.2 == "" | BosEvt$Home.Address.2 == " "] <- NA;
BosEvt$Home.Address.2 <- tolower(as.character(BosEvt$Home.Address.2));

BosEvt$Company[BosEvt$Company == "" | BosEvt$Company == " "] <- NA;
BosEvt$Company <- tolower(as.character(BosEvt$Company));

BosEvt$Home.City[BosEvt$Home.City == "" | BosEvt$Home.City == " "] <- NA;
BosEvt$Home.City <- tolower(as.character(BosEvt$Home.City));

BosEvt$Home.State[BosEvt$Home.State == "" | BosEvt$Home.State == " "] <- NA;
BosEvt$Home.State <- tolower(as.character(BosEvt$Home.State));

BosEvt$Home.Zip[BosEvt$Home.Zip == "" | BosEvt$Home.Zip == " "] <- NA;
BosEvt$Home.Zip <- tolower(as.character(BosEvt$Home.Zip));

BosEvt$Home.Country[BosEvt$Home.Country == "" | BosEvt$Home.Country == " "] <- NA;
BosEvt$Home.Country <- tolower(as.character(BosEvt$Home.Country));

dim(BosEvt);
```

## 8 Use email to append the ID.
```{r useEmail}
dim(unique(na.omit(All[c("EMAIL.ADDRESS")])));
dim(unique(na.omit(All[c("MEMBER.ID")])));
sub1 <- subset(All, !(is.na(All$EMAIL.ADDRESS))& !(is.na(All$MEMBER.ID)));
dim(unique(sub1[c("EMAIL.ADDRESS", "MEMBER.ID")]));
#In BosEvt, there is no Email == NA.
dim(filter(BosEvt, is.na(BosEvt$Email)));
table(BosEvt$Email %in% All$EMAIL.ADDRESS);

EmailGroup <- split(All, All$EMAIL.ADDRESS);

# to see in membership file if same email address has more than one ID.
b1 <- data.frame(MEMBER.ID = numeric(), FIRST.NAME = character(),MIDDLE.NAME = character(), LAST.NAME = character(),
                      LABEL.NAME = character(), 
                      EMAIL.ADDRESS = character(), FULL.NAME = character());
b1 <- do.call(rbind,lapply(EmailGroup, function(x) {
        if (length(unique(x$MEMBER.ID)) > 1)
                {data.frame(MEMBER.ID = x$MEMBER.ID,
                           FIRST.NAME = x$FIRST.NAME,
                           MIDDLE.NAME  = x$MIDDLE.NAME,
                           LAST.NAME = x$LAST.NAME,
                           LABEL.NAME = x$LABEL.NAME,
                           EMAIL.ADDRESS = x$EMAIL.ADDRESS,
                           FULL.NAME = x$FULL.NAME)}
        else
                data.frame = NULL}
        ));
dim(b1);

AMAEmailUnique <- unique(na.omit(All[c("MEMBER.ID","EMAIL.ADDRESS")]));
MERGE1 <- merge(BosEvt, AMAEmailUnique, by.x = "Email",by.y = "EMAIL.ADDRESS",all.x = TRUE, all.y = FALSE);
dim(MERGE1[!(is.na(MERGE1$MEMBER.ID)),]);
dim(unique(MERGE1["MEMBER.ID"]));
```

## 9. Use first name, last name and company to append ID.
```{r FirstLastNameCompany}
NameCompany <-  unique(na.omit(All[c("MEMBER.ID", "FIRST.NAME","LAST.NAME", "COMPANY.NAME")]));
MERGE2 <- merge(MERGE1, NameCompany, by.x = c("First.Name","Last.Name", "Company"), by.y = c("FIRST.NAME","LAST.NAME", "COMPANY.NAME"), all.x = TRUE, all.y=FALSE);

dim(MERGE2[!(is.na(MERGE2$MEMBER.ID.y)),]);
dim(MERGE2[is.na(MERGE2$MEMBER.ID.x) & !(is.na(MERGE2$MEMBER.ID.y)),]);
dim(MERGE2[!(is.na(MERGE2$MEMBER.ID.x)) & !(is.na(MERGE2$MEMBER.ID.y)),])

table(MERGE2$MEMBER.ID.y == MERGE2$MEMBER.ID.x);
which(!(MERGE2$MEMBER.ID.y == MERGE2$MEMBER.ID.x));
MERGE2[which(!(MERGE2$MEMBER.ID.y == MERGE2$MEMBER.ID.x)),]$MEMBER.ID.y <- NA;
# 1931 1932 1934 1935, should choose ID.x, not ID.y


dim(unique(MERGE2["MEMBER.ID.y"]));
table(unique(na.omit(MERGE2$MEMBER.ID.y)) %in% unique(na.omit(MERGE2$MEMBER.ID.x)));
```
## 10. Use first name, last name and address 1 to append ID.
```{r FirstLastNameAddress1}
NameAdrs1 <-  unique(na.omit(All[c("MEMBER.ID", "FIRST.NAME","LAST.NAME", "PRIMARY.ADDRESS.1")]));
MERGE3 <- merge(MERGE2, NameAdrs1, by.x = c("First.Name","Last.Name", "Home.Address.1"), by.y = c("FIRST.NAME","LAST.NAME", "PRIMARY.ADDRESS.1"), all.x = TRUE, all.y=FALSE);

colnames(MERGE3)[which(names(MERGE3) == "MEMBER.ID")] <- "MEMBER.ID.z";

dim(MERGE3[!(is.na(MERGE3$MEMBER.ID.z)),]);
dim(MERGE3[is.na(MERGE3$MEMBER.ID.x) & is.na(MERGE3$MEMBER.ID.y) & !(is.na(MERGE3$MEMBER.ID.z)),]);

dim(MERGE3[(!(is.na(MERGE3$MEMBER.ID.x))) & (!(is.na(MERGE3$MEMBER.ID.z))),]);
table(MERGE3$MEMBER.ID.z == MERGE3$MEMBER.ID.x);

dim(MERGE3[!(is.na(MERGE3$MEMBER.ID.y)) & !(is.na(MERGE3$MEMBER.ID.z)),]);
table(MERGE3$MEMBER.ID.z == MERGE3$MEMBER.ID.y);

table(unique(na.omit(MERGE3$MEMBER.ID.z)) %in% unique(na.omit(MERGE3$MEMBER.ID.x)));
table(unique(na.omit(MERGE3$MEMBER.ID.z)) %in% unique(na.omit(MERGE3$MEMBER.ID.y)));
table((unique(na.omit(MERGE3$MEMBER.ID.z)) %in% unique(na.omit(MERGE3$MEMBER.ID.x))) & (unique(na.omit(MERGE3$MEMBER.ID.z)) %in% unique(na.omit(MERGE3$MEMBER.ID.y))));
table(!(unique(na.omit(MERGE3$MEMBER.ID.z)) %in% unique(na.omit(MERGE3$MEMBER.ID.x))) & !(unique(na.omit(MERGE3$MEMBER.ID.z)) %in% unique(na.omit(MERGE3$MEMBER.ID.y))));

```

## 11. Use first name, last name and address 2 to append ID.
```{r FirstLastNameAddress2}
NameAdrs2 <-  unique(na.omit(All[c("MEMBER.ID", "FIRST.NAME","LAST.NAME", "PRIMARY.ADDRESS.2")]));
MERGE4 <- merge(MERGE3, NameAdrs2, by.x = c("First.Name","Last.Name", "Home.Address.2"), by.y = c("FIRST.NAME","LAST.NAME", "PRIMARY.ADDRESS.2"), all.x = TRUE, all.y=FALSE);

colnames(MERGE4)[which(names(MERGE4) == "MEMBER.ID")] <- "MEMBER.ID.x1";

dim(MERGE4[!(is.na(MERGE4$MEMBER.ID.x1)),]);
# MERGE4 only add one ID, and the rest has no ID conflict.
dim(MERGE4[is.na(MERGE4$MEMBER.ID.x) & is.na(MERGE4$MEMBER.ID.y) & is.na(MERGE4$MEMBER.ID.z) & 
                   (!is.na(MERGE4$MEMBER.ID.x1)),]);

```
## 12. Use last name and company to append ID.
```{r LastNameCompany}
LastNameCompany <-  unique(na.omit(All[c("MEMBER.ID", "LAST.NAME", "COMPANY.NAME")]));
MERGE5 <- merge(MERGE4, LastNameCompany, by.x = c("Last.Name", "Company"), by.y = c("LAST.NAME", "COMPANY.NAME"), all.x = TRUE, all.y = FALSE);

# nrow(MERGE5) is larger than BosEvt, which means that there are ones with the sanme last name and company, but different ID. 
# These are the ones with the sanme last name and company, but different ID.
selectDup <- LastNameCompany[duplicated(LastNameCompany[,c("LAST.NAME", "COMPANY.NAME")])|duplicated(LastNameCompany[,c("LAST.NAME", "COMPANY.NAME")], fromLast=TRUE),];
Dup1 <- MERGE5[MERGE5$Last.Name == "bozas" & MERGE5$Company == "polvora advertising",];
# Dup2 and Dup3 are empty.
Dup2 <- MERGE5[MERGE5$Last.Name == "deiana" & MERGE5$Company == "worcester polytechnic institute",];
 Dup3 <- MERGE5[MERGE5$Last.Name == "napper rogers" & MERGE5$Company == "johnson & wales university",];

LNC2 <- LastNameCompany[!(LastNameCompany$LAST.NAME == "bozas" & LastNameCompany$COMPANY.NAME == "polvora advertising"),];
MERGE5 <- merge(MERGE4, LNC2, by.x = c("Last.Name", "Company"), by.y = c("LAST.NAME", "COMPANY.NAME"), all.x = TRUE, all.y = FALSE);

colnames(MERGE5)[which(names(MERGE5) == "MEMBER.ID")] <- "MEMBER.ID.y1";

dim(MERGE5[!(is.na(MERGE5$MEMBER.ID.y1)),]);

table(MERGE5$MEMBER.ID.y1 == MERGE5$MEMBER.ID.x);

MERGE5[which(!(MERGE5$MEMBER.ID.y1 == MERGE5$MEMBER.ID.x)),]$MEMBER.ID.y1 <- NA;
which(!(MERGE5$MEMBER.ID.y1 == MERGE5$MEMBER.ID.y));
which(!(MERGE5$MEMBER.ID.y1 == MERGE5$MEMBER.ID.z));
which(!(MERGE5$MEMBER.ID.y1 == MERGE5$MEMBER.ID.x1));

dim(MERGE5[is.na(MERGE5$MEMBER.ID.x) & is.na(MERGE5$MEMBER.ID.y) & is.na(MERGE5$MEMBER.ID.z) & 
                    is.na(MERGE5$MEMBER.ID.x1) & (!is.na(MERGE5$MEMBER.ID.y1)),]);
```

## 13. Check if there are more than one ID for each row.
```{r CheckIDs}
MERGE5$count <- apply(MERGE5[c("MEMBER.ID.x", "MEMBER.ID.y", "MEMBER.ID.z", "MEMBER.ID.x1", "MEMBER.ID.y1")],1,function(x) length(unique(na.omit(x))));

# 1706 ID, no conflict.
table(MERGE5$count);
# write.csv(MERGE5, "MERGE.csv", row.names = FALSE, na = "");

```

```{r writeMergeFile}
MERGE6 <- MERGE5[MERGE5$count == 1,];
ids <- apply(MERGE6[c("MEMBER.ID.x", "MEMBER.ID.y", "MEMBER.ID.z", "MEMBER.ID.x1", "MEMBER.ID.y1")],1,function(x) unique(na.omit(x)));

MERGE6$MEMBER.ID <- ids;

MERGE6 <-MERGE6[,!names(MERGE6) %in% c("MEMBER.ID.x", "MEMBER.ID.y", "MEMBER.ID.z", "MEMBER.ID.x1", "MEMBER.ID.y1", "count")]

write.csv(MERGE6, "MERGEID.csv", row.names = FALSE);
```

```{r addIDforBosEvt}
BosEvtQC <- BosEvt;
idEvt <- 1:nrow(BosEvtQC);
BosEvtQC$idEvt <- idEvt;
```


```{r QCEmail}
colnames(BosEvtQC)[which(names(BosEvtQC) == "Email")] <- "EmailEvt";

EmlUn <- unique(na.omit(All[c("MEMBER.ID","EMAIL.ADDRESS")]));
# idMem is the row number in membership dataset All.
rowMem <- as.numeric(rownames(EmlUn));
EmlUn$idMem <- rowMem;

colnames(EmlUn)[which(names(EmlUn) == "EMAIL.ADDRESS")] <- "EMAIL.ADDRESSMem";
colnames(EmlUn)[which(names(EmlUn) =="MEMBER.ID")] <- "MEMBER.ID.x";

Merge1 <- merge(BosEvtQC[,c("EmailEvt","idEvt")], EmlUn, by.x = "EmailEvt", by.y = "EMAIL.ADDRESSMem", all.x = FALSE, all.y = FALSE);

Merge1$EMAIL.ADDRESSMem <- EmlUn[match(Merge1$idMem, EmlUn$idMem), "EMAIL.ADDRESSMem"];
Merge1 <- Merge1[,c("idEvt", "EmailEvt", "idMem", "EMAIL.ADDRESSMem", "MEMBER.ID.x")]
Merge1 <- Merge1[order(Merge1$idEvt),];

# write.xlsx(Merge1, "Merge_ID_x.xlsx", row.names = FALSE);
```

```{r QCfirstlastNameCompany}
colnames(BosEvtQC)[which(names(BosEvtQC) == "First.Name")] <- "First.NameEvt";
colnames(BosEvtQC)[which(names(BosEvtQC) == "Last.Name")] <- "Last.NameEvt";
colnames(BosEvtQC)[which(names(BosEvtQC) == "Company")] <- "CompanyEvt";

FLCUn <- unique(na.omit(All[c("MEMBER.ID","FIRST.NAME", "LAST.NAME", "COMPANY.NAME")]));

rowMem <- as.numeric(rownames(FLCUn));
# idMem is the row number in membership dataset All. 
FLCUn$idMem <- rowMem;

colnames(FLCUn)[which(names(FLCUn) == "FIRST.NAME")] <- "FIRST.NAMEMem";
colnames(FLCUn)[which(names(FLCUn) == "LAST.NAME")] <- "LAST.NAMEMem";
colnames(FLCUn)[which(names(FLCUn) == "COMPANY.NAME")] <- "COMPANY.NAMEMem";
colnames(FLCUn)[which(names(FLCUn) =="MEMBER.ID")] <- "MEMBER.ID.y";

Merge2 <- merge(BosEvtQC[, c("First.NameEvt","Last.NameEvt","CompanyEvt","idEvt")], FLCUn, by.x = c("First.NameEvt", "Last.NameEvt", "CompanyEvt"), by.y = c("FIRST.NAMEMem", "LAST.NAMEMem",  "COMPANY.NAMEMem"), all.x = FALSE, all.y = FALSE);

Merge2$FIRST.NAMEMem <- FLCUn[match(Merge2$idMem, FLCUn$idMem), "FIRST.NAMEMem"];
Merge2$LAST.NAMEMem <- FLCUn[match(Merge2$idMem, FLCUn$idMem), "LAST.NAMEMem"];
Merge2$COMPANY.NAMEMem <- FLCUn[match(Merge2$idMem, FLCUn$idMem), "COMPANY.NAMEMem"];
Merge2 <- Merge2[,c("idEvt", "First.NameEvt", "Last.NameEvt","CompanyEvt","idMem", "FIRST.NAMEMem", "LAST.NAMEMem","COMPANY.NAMEMem","MEMBER.ID.y")];

Merge2 <- Merge2[order(Merge2$idEvt),];
# write.xlsx(Merge2, "Merge_ID_y.xlsx", row.names = FALSE);
```

```{r QCFirstLastNameAddress1}

colnames(BosEvtQC)[which(names(BosEvtQC) == "Home.Address.1")] <- "Home.Address.1Evt";

FLA1Un <- unique(na.omit(All[c("MEMBER.ID","FIRST.NAME","LAST.NAME", "PRIMARY.ADDRESS.1")]));

rowMem <- as.numeric(rownames(FLA1Un));
# idMem is the row number in membership dataset All. 
FLA1Un$idMem <- rowMem;

colnames(FLA1Un)[which(names(FLA1Un) == "FIRST.NAME")] <- "FIRST.NAMEMem";
colnames(FLA1Un)[which(names(FLA1Un) == "LAST.NAME")] <- "LAST.NAMEMem";
colnames(FLA1Un)[which(names(FLA1Un) == "PRIMARY.ADDRESS.1")] <- "PRIMARY.ADDRESS.1Mem";
colnames(FLA1Un)[which(names(FLA1Un) =="MEMBER.ID")] <- "MEMBER.ID.z";

Merge3 <- merge(BosEvtQC[, c("First.NameEvt","Last.NameEvt", "Home.Address.1Evt","idEvt")], FLA1Un, by.x = c("First.NameEvt","Last.NameEvt", "Home.Address.1Evt"), by.y = c("FIRST.NAMEMem","LAST.NAMEMem",  "PRIMARY.ADDRESS.1Mem"), all.x = FALSE, all.y = FALSE);

Merge3$FIRST.NAMEMem <- FLA1Un[match(Merge3$idMem, FLA1Un$idMem), "FIRST.NAMEMem"];
Merge3$LAST.NAMEMem <- FLA1Un[match(Merge3$idMem, FLA1Un$idMem), "LAST.NAMEMem"];
Merge3$PRIMARY.ADDRESS.1Mem <-FLA1Un[match(Merge3$idMem, FLA1Un$idMem), "PRIMARY.ADDRESS.1Mem"];
Merge3 <- Merge3[,c("idEvt", "First.NameEvt", "Last.NameEvt","Home.Address.1Evt","idMem", "FIRST.NAMEMem", "LAST.NAMEMem","PRIMARY.ADDRESS.1Mem","MEMBER.ID.z")];

Merge3 <- Merge3[order(Merge3$idEvt),];
# write.xlsx(Merge3, "Merge_ID_z.xlsx", row.names = FALSE);
```

```{r QCFirstLastNameAddress2}

colnames(BosEvtQC)[which(names(BosEvtQC) == "Home.Address.2")] <- "Home.Address.2Evt";

FLA2Un <- unique(na.omit(All[c("MEMBER.ID","FIRST.NAME","LAST.NAME", "PRIMARY.ADDRESS.2")]));

rowMem <- as.numeric(rownames(FLA2Un));
# idMem is the row number in membership dataset All. 
FLA2Un$idMem <- rowMem;

colnames(FLA2Un)[which(names(FLA2Un) == "FIRST.NAME")] <- "FIRST.NAMEMem";
colnames(FLA2Un)[which(names(FLA2Un) == "LAST.NAME")] <- "LAST.NAMEMem";
colnames(FLA2Un)[which(names(FLA2Un) == "PRIMARY.ADDRESS.2")] <- "PRIMARY.ADDRESS.2Mem";
colnames(FLA2Un)[which(names(FLA2Un) =="MEMBER.ID")] <- "MEMBER.ID.x1";

Merge4 <- merge(BosEvtQC[, c("First.NameEvt","Last.NameEvt", "Home.Address.2Evt","idEvt")], FLA2Un, by.x = c("First.NameEvt","Last.NameEvt", "Home.Address.2Evt"), by.y = c("FIRST.NAMEMem","LAST.NAMEMem",  "PRIMARY.ADDRESS.2Mem"), all.x = FALSE, all.y = FALSE);

Merge4$FIRST.NAMEMem <- FLA2Un[match(Merge4$idMem, FLA2Un$idMem), "FIRST.NAMEMem"];
Merge4$LAST.NAMEMem <- FLA2Un[match(Merge4$idMem, FLA2Un$idMem), "LAST.NAMEMem"];
Merge4$PRIMARY.ADDRESS.2Mem <-FLA2Un[match(Merge4$idMem, FLA2Un$idMem), "PRIMARY.ADDRESS.2Mem"];
Merge4 <- Merge4[,c("idEvt", "First.NameEvt", "Last.NameEvt","Home.Address.2Evt","idMem", "FIRST.NAMEMem", "LAST.NAMEMem","PRIMARY.ADDRESS.2Mem","MEMBER.ID.x1")];

Merge4 <- Merge4[order(Merge4$idEvt),];
# write.xlsx(Merge4, "Merge_ID_x1.xlsx", row.names = FALSE);
```

```{r QClastNameCompany}
LCUn <- unique(na.omit(All[c("MEMBER.ID", "LAST.NAME", "COMPANY.NAME")]));

LCUn <- LCUn[!(LCUn$LAST.NAME == "bozas" & LCUn$COMPANY.NAME == "polvora advertising"),];

rowMem <- as.numeric(rownames(LCUn));
# idMem is the row number in membership dataset All. 
LCUn$idMem <- rowMem;

colnames(LCUn)[which(names(LCUn) == "LAST.NAME")] <- "LAST.NAMEMem";
colnames(LCUn)[which(names(LCUn) == "COMPANY.NAME")] <- "COMPANY.NAMEMem";
colnames(LCUn)[which(names(LCUn) =="MEMBER.ID")] <- "MEMBER.ID.y1";

Merge5 <- merge(BosEvtQC[, c("Last.NameEvt","CompanyEvt","idEvt")], LCUn, by.x = c( "Last.NameEvt", "CompanyEvt"), by.y = c("LAST.NAMEMem",  "COMPANY.NAMEMem"), all.x = FALSE, all.y = FALSE);

Merge5$LAST.NAMEMem <- LCUn[match(Merge5$idMem, LCUn$idMem), "LAST.NAMEMem"];
Merge5$COMPANY.NAMEMem <- LCUn[match(Merge5$idMem, LCUn$idMem), "COMPANY.NAMEMem"];
Merge5 <- Merge5[,c("idEvt", "Last.NameEvt","CompanyEvt","idMem",  "LAST.NAMEMem","COMPANY.NAMEMem","MEMBER.ID.y1")];

Merge5 <- Merge5[order(Merge5$idEvt),];
# write.xlsx(Merge5, "Merge_ID_y1.xlsx", row.names = FALSE);
```


```{r SaveEvtMem}
# xlcFreeMemory() : to clear java memory
# add id to BosEvt and All, then save them.
BosEvtID <- BosEvt;
BosEvtID <- cbind(idEvt = 1:nrow(BosEvtID), BosEvtID);
# write.xlsx(BosEvtID, "BosEvtwithID.xlsx", row.names = FALSE,showNA = FALSE);

AllID <- All;
AllID <- cbind(idMem = 1:nrow(AllID), AllID);
# write.xlsx(AllID, "AllMembershipwithID.xlsx", row.names = FALSE,showNA = FALSE);
```





