---
title: "American Marketing Association (AMA) membership information"
output: pdf_document
---
This data analysis focuses on loading the AMA membership xlsx files from September 
2013 to september 2016, missing the file from August, 2015, combining them together, and label the members who have renewed their membership by 1.

## 1. Note
This file needs to set the current working directory to where it contains the "New AMA membership" folder. To run this file, instead of press the "Knit HTML" button in R Studio, type "rmarkdown::render("AMAMembership.Rmd")" in the console. This will knit in the current session instead of a background session, so that you can play with the varialbes in console. This HTML will be updated, but you have to click open it.

```{r removeVariables}
rm(list=ls(all=TRUE));
```
```{r setup}
library(knitr)
opts_chunk$set(echo = TRUE,tidy = TRUE);
# opts_chunk$set(cache.path = paste(getwd(), "/AMAMembership_cache/html", sep=""));
# echo = TRUE: shows the R code in the output document
# cache = TRUE: when evaluating code chunks, the cached chunks are skipped, 
# but the objects created in these chunks are loaded from previously saved database
# autodep = TRUE: figure out the dependencies among chunks automatically
# by analyzing the global variables in the code (may not be reliable)
# include = FALSE: nothing will be written into the output document, 
# but the code is still evaluated and plot files are generated if there are
# any plots in the chunk
```
## 2. Read in the data files (xlsx) into R studio.
```{r results="hide"}
library(xlsx)
library(dplyr)
library(lubridate)
library(zoo)
```

```{r ReadInSep2013,cache=TRUE}
Sep2013<-read.xlsx(paste(getwd(),"/New AMA Membership/2013 09_September AMA Membership_v2.xlsx",sep=""), sheetIndex = 1)
```

```{r ReadInOct2013,cache=TRUE}
Oct2013<-read.xlsx(paste(getwd(),"/New AMA Membership/2013 10_October AMA Membership_v2.xlsx",sep=""), sheetIndex = 1)
```
```{r ReadInNov2013,cache=TRUE}
Nov2013<-read.xlsx(paste(getwd(),"/New AMA Membership/2013 11_November AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInDec2013,cache=TRUE}
Dec2013<-read.xlsx(paste(getwd(),"/New AMA Membership/2013 12_December AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInJan2014,cache=TRUE}
Jan2014<-read.xlsx(paste(getwd(),"/New AMA Membership/2014 01_January AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInFeb2014,cache=TRUE}
Feb2014<-read.xlsx(paste(getwd(),"/New AMA Membership/2014 02_February AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInMar2014,cache=TRUE}
Mar2014<-read.xlsx(paste(getwd(),"/New AMA Membership/2014 03_March AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInApr2014,cache=TRUE}
Apr2014<-read.xlsx(paste(getwd(),"/New AMA Membership/2014 04_April AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInMay2014,cache=TRUE}
May2014<-read.xlsx(paste(getwd(),"/New AMA Membership/2014 05_May AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInJun2014,cache=TRUE}
Jun2014<-read.xlsx(paste(getwd(),"/New AMA Membership/2014 06_June AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInJul2014,cache=TRUE}
Jul2014<-read.xlsx(paste(getwd(),"/New AMA Membership/2014 07_July AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInAug2014,cache=TRUE}
Aug2014<-read.xlsx(paste(getwd(),"/New AMA Membership/2014 08_August AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInSep2014,cache=TRUE}
Sep2014<-read.xlsx(paste(getwd(),"/New AMA Membership/2014 09_September AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInOct2014,cache=TRUE}
Oct2014<-read.xlsx(paste(getwd(),"/New AMA Membership/2014 10_October AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInNov2014,cache=TRUE}
Nov2014<-read.xlsx(paste(getwd(),"/New AMA Membership/2014 11_November AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInDec2014,cache=TRUE}
Dec2014<-read.xlsx(paste(getwd(),"/New AMA Membership/2014 12_December AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInJan2015,cache=TRUE}
Jan2015<-read.xlsx(paste(getwd(),"/New AMA Membership/2015 01_January AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInFeb2015,cache=TRUE}
Feb2015<-read.xlsx(paste(getwd(),"/New AMA Membership/2015 02_February AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```

```{r ReadInMar2015,cache=TRUE}
Mar2015<-read.xlsx(paste(getwd(),"/New AMA Membership/2015 03_March AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInApr2015,cache=TRUE}
Apr2015<-read.xlsx(paste(getwd(),"/New AMA Membership/2015 04_April AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInMay2015,cache=TRUE}
May2015<-read.xlsx(paste(getwd(),"/New AMA Membership/2015 05_May AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInJun2015,cache=TRUE}
Jun2015<-read.xlsx(paste(getwd(),"/New AMA Membership/2015 06_June AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInJul2015,cache=TRUE}
Jul2015<-read.xlsx(paste(getwd(),"/New AMA Membership/2015 07_July AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInSep2015,cache=TRUE}
Sep2015<-read.xlsx(paste(getwd(),"/New AMA Membership/2015 09_September AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInOct2015,cache=TRUE}
Oct2015<-read.xlsx(paste(getwd(),"/New AMA Membership/2015 10_October AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInNov2015,cache=TRUE}
Nov2015<-read.xlsx(paste(getwd(),"/New AMA Membership/2015 11_November AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInDec2015,cache=TRUE}
Dec2015<-read.xlsx(paste(getwd(),"/New AMA Membership/2015 12_December AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInJan2016,cache=TRUE}
Jan2016<-read.xlsx(paste(getwd(),"/New AMA Membership/2016 01_January AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInFeb2016,cache=TRUE}
Feb2016<-read.xlsx(paste(getwd(),"/New AMA Membership/2016 02_February AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInMar2016,cache=TRUE}
Mar2016<-read.xlsx(paste(getwd(),"/New AMA Membership/2016 03_March AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInApr2016,cache=TRUE}
Apr2016<-read.xlsx(paste(getwd(),"/New AMA Membership/2016 04_April AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```

```{r ReadInMay2016,cache=TRUE}
May2016<-read.xlsx(paste(getwd(),"/New AMA Membership/2016 05_May AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInJun2016,cache=TRUE}
Jun2016<-read.xlsx(paste(getwd(),"/New AMA Membership/2016 06_June AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInJul2016,cache=TRUE}
Jul2016<-read.xlsx(paste(getwd(),"/New AMA Membership/2016 07_July AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInAug2016,cache=TRUE}
Aug2016<-read.xlsx(paste(getwd(),"/New AMA Membership/2016 08_August AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
```{r ReadInSep2016,cache=TRUE}
Sep2016<-read.xlsx(paste(getwd(),"/New AMA Membership/2016 09_September AMA Membership_v2.xlsx",sep=""), sheetIndex = 1);
```
## 3. Convert ID to numeric type.
```{r convertID,results="hide"}
# Convert MEMBER.ID to numeric type and all the dates to date type.
# NAMES2 does not include Nov2013 file.
NAMES2<-c("Sep2013","Oct2013","Dec2013","Jan2014","Feb2014","Mar2014",
          "Apr2014","May2014","Jun2014","Jul2014","Aug2014","Sep2014",
          "Oct2014","Nov2014","Dec2014","Jan2015","Feb2015","Mar2015",
          "Apr2015","May2015","Jun2015","Jul2015","Sep2015","Oct2015",
          "Nov2015","Dec2015","Jan2016","Feb2016","Mar2016","Apr2016",
          "May2016","Jun2016","Jul2016","Aug2016","Sep2016");
# check if there is NA value before converting the MEMBER.ID
for (i in NAMES2)
{j = get(i);
print(dim(j[is.na(j$MEMBER.ID),])); 
j$MEMBER.ID <- as.numeric(paste(j$MEMBER.ID));
assign(i,j);
}
# check if there is NA value after converting the MEMBER.ID to numeric type.
for (i in NAMES2)
{j = get(i);
print(dim(j[is.na(j$MEMBER.ID),]));
str(j$MEMBER.ID);
}
```

## 4. Convert the date to date type.
```{r convertDate,results="hide"}
# These are the files with date format: "%Y-%m-%d"
NAMES3 <-c("Sep2013","Oct2014","Nov2014","Dec2014","Jan2015","Feb2015",
           "Mar2015","Apr2015","May2015","Jun2015","Jul2015","Sep2015",
           "Oct2015","Nov2015","Dec2015","Jan2016","Feb2016","Mar2016",
           "Apr2016","May2016","Jun2016","Jul2016","Aug2016","Sep2016");

# These are the files with date format: "%m/%d/%Y"
NAMES4<-c("Oct2013","Dec2013","Jan2014","Feb2014","Mar2014","Apr2014",
          "May2014","Jun2014","Jul2014","Aug2014","Sep2014");

# Check if there is NA value before converting MEMBER.SINCE.DATE
for (i in NAMES3)
{j = get(i);
print(dim(j[is.na(j$MEMBER.SINCE.DATE),]));
j$MEMBER.SINCE.DATE <- as.Date(j$MEMBER.SINCE.DATE,"%Y-%m-%d");
assign(i,j);
}

# Check if there is NA value after converting MEMBER.SINCE.DATE
for (i in NAMES3)
{j = get(i);
print(dim(j[is.na(j$MEMBER.SINCE.DATE),]));
str(j$MEMBER.SINCE.DATE);
}
# Check if there is NA value before converting MEMBER.SINCE.DATE
for (i in NAMES4)
{j = get(i);
print(dim(j[is.na(j$MEMBER.SINCE.DATE),]));
j$MEMBER.SINCE.DATE <- as.Date(j$MEMBER.SINCE.DATE,"%m/%d/%Y");
assign(i,j);
}
# Check if there is NA value after converting MEMBER.SINCE.DATE
for (i in NAMES4)
{j = get(i);
print(dim(j[is.na(j$MEMBER.SINCE.DATE),]));
str(j$MEMBER.SINCE.DATE);
}

# Check if there is NA value before converting EXPIRATION.DATE
for (i in NAMES3)
{j = get(i);
print(dim(j[is.na(j$EXPIRATION.DATE),]));
j$EXPIRATION.DATE <- as.Date(j$EXPIRATION.DATE,"%Y-%m-%d");
assign(i,j);
}
# Check if there is NA value after converting EXPIRATION.DATE
for (i in NAMES3)
{j = get(i);
print(dim(j[is.na(j$EXPIRATION.DATE),]));
str(j$EXPIRATION.DATE);
}
# Check if there is NA value before converting EXPIRATION.DATE
for (i in NAMES4)
{j = get(i);
print(dim(j[is.na(j$EXPIRATION.DATE),]));
j$EXPIRATION.DATE <- as.Date(j$EXPIRATION.DATE,"%m/%d/%Y");
assign(i,j);
}
# Check if there is NA value after converting EXPIRATION.DATE
for (i in NAMES4)
{j = get(i);
print(dim(j[is.na(j$EXPIRATION.DATE),]));
str(j$EXPIRATION.DATE);
}

# Check if there is NA value before converting DATE.PULLED
for (i in NAMES3)
{j = get(i);
print(dim(j[is.na(j$DATE.PULLED),]));
j$DATE.PULLED <- as.Date(j$DATE.PULLED,"%Y-%m-%d");
assign(i,j);
}
# Check if there is NA value after converting DATE.PULLED
for (i in NAMES3)
{j = get(i);
print(dim(j[is.na(j$DATE.PULLED),]));
str(j$DATE.PULLED);
}
# Check if there is NA value before converting DATE.PULLED
for (i in NAMES4)
{j = get(i);
print(dim(j[is.na(j$DATE.PULLED),]));
j$DATE.PULLED <- as.Date(j$DATE.PULLED,"%m/%d/%Y");
assign(i,j);
}
# Check if there is NA value after converting DATE.PULLED
for (i in NAMES4)
{j = get(i);
print(dim(j[is.na(j$DATE.PULLED),]));
str(j$DATE.PULLED);
}

# The codes below are used to comapre names and class types of different files.
# table(names(Sep2013) %in% names(Oct2013))["FALSE"];
# names(Sep2013)[which(sapply(Sep2013,class)!="factor")];
# for (i in NAMES2){j=get(i);print(i);print(class(j$COMMUNICATION.CHANGE.DATE))}

# NAMES5 are the ones that these four columns need to be converted 
# to date type:"ADDRESS.CHANGE.DATE", "COMMUNICATION.CHANGE.DATE",
# "STUDENT.GRADUATION.DATE", "DATE.LAST.MODIFIED".
# It turns out that NAMES5 is the same as NAMES4
NAMES5 <-c("Oct2013","Dec2013","Jan2014","Feb2014","Mar2014",
           "Apr2014","May2014","Jun2014","Jul2014","Aug2014","Sep2014");

# Check the number of rows of the file and the number of empty values of 
# "ADDRESS.CHANGE.DATE" before converting.
for (i in NAMES5)
{j = get(i);
cat(paste(dim(j)[1],dim(j[j$ADDRESS.CHANGE.DATE=="",])[1],sep="\t"),"\n");
j$ADDRESS.CHANGE.DATE <- as.Date(j$ADDRESS.CHANGE.DATE,"%m/%d/%Y");
assign(i,j);
}
# Check the number of rows of the file and the number of NA values of 
# "ADDRESS.CHANGE.DATE" after converting.
for (i in NAMES5)
{j = get(i);
cat(paste(dim(j)[1],dim(j[is.na(j$ADDRESS.CHANGE.DATE),])[1],sep="\t"),"\n");
print(head(unique(j$ADDRESS.CHANGE.DATE)));
}

# Check the number of rows of the file and the number of empty values of 
# "COMMUNICATION.CHANGE.DATE" before converting.
for (i in NAMES5)
{j = get(i);
cat(paste(dim(j)[1],dim(j[j$COMMUNICATION.CHANGE.DATE=="",])[1],sep="\t"),"\n");
j$COMMUNICATION.CHANGE.DATE <- as.Date(j$COMMUNICATION.CHANGE.DATE,"%m/%d/%Y");
assign(i,j);
}

# Check the number of rows of the file and the number of NA values of 
# "COMMUNICATION.CHANGE.DATE" after converting.
for (i in NAMES5)
{j = get(i);
cat(paste(dim(j)[1],dim(j[is.na(j$COMMUNICATION.CHANGE.DATE),])[1],sep="\t"),"\n");
print(head(unique(j$COMMUNICATION.CHANGE.DATE)));
}

# NAMES6 are the ones whose COMMUNICATION.CHANGE.DATE are logic type.
NAMES6 <-c("May2015","Jun2015","Jul2015","Sep2015","Oct2015",
           "Dec2015","Jan2016","Mar2016","Apr2016","May2016","Jul2016",
           "Aug2016");

# Check the number of rows of the file and the number of empty values of 
# "COMMUNICATION.CHANGE.DATE" before converting.
for (i in NAMES6)
{j = get(i);
cat(paste(dim(j)[1],dim(j[j$COMMUNICATION.CHANGE.DATE=="",])[1],sep="\t"),"\n");
j$COMMUNICATION.CHANGE.DATE <- as.Date(as.character(j$COMMUNICATION.CHANGE.DATE),"%m/%d/%Y");
assign(i,j);
}
# Check the number of rows of the file and the number of NA values of 
# "COMMUNICATION.CHANGE.DATE" after converting.
for (i in NAMES6)
{j = get(i);
cat(paste(dim(j)[1],dim(j[is.na(j$COMMUNICATION.CHANGE.DATE),])[1],sep="\t"),"\n");
print(head(unique(j$COMMUNICATION.CHANGE.DATE)));
}

# Check the number of rows of the file and the number of empty values of 
# "STUDENT.GRADUATE.DATE" before converting.
for (i in NAMES5)
{j = get(i);
cat(paste(dim(j)[1],dim(j[j$STUDENT.GRADUATION.DATE=="",])[1],sep="\t"),"\n");
j$STUDENT.GRADUATION.DATE <- as.Date(j$STUDENT.GRADUATION.DATE,"%m/%d/%Y");
assign(i,j);
}
# Check the number of rows of the file and the number of NA values of 
# "STUDENT.GRADUATE.DATE" after converting.
for (i in NAMES5)
{j = get(i);
cat(paste(dim(j)[1],dim(j[is.na(j$STUDENT.GRADUATION.DATE),])[1],sep="\t"),"\n");
print(head(unique(j$STUDENT.GRADUATION.DATE)));
}

# Check the number of rows of the file and the number of empty values of 
# "DATE.LAST.MODIFIED" before converting.
for (i in NAMES5)
{j = get(i);
cat(paste(dim(j)[1],dim(j[is.na(j$DATE.LAST.MODIFIED),])[1],sep="\t"),"\n");
j$DATE.LAST.MODIFIED <- as.Date(j$DATE.LAST.MODIFIED,"%m/%d/%Y");
assign(i,j);
}
# Check the number of rows of the file and the number of empty values of 
# "DATE.LAST.MODIFIED" after converting.
for (i in NAMES5)
{j = get(i);
cat(paste(dim(j)[1],dim(j[is.na(j$DATE.LAST.MODIFIED),])[1],sep="\t"),"\n");
print(head(unique(j$DATE.LAST.MODIFIED)));
}
```

## 5. Merge all the files.
```{r mergeAllFiles}
# Merge all the files except Nov2013.

identical(Sep2015$COMPANY.NAME,Sep2015$COMPANY.NAME.1);
Sep2015<-subset(Sep2015,select= (names(Sep2015) != "COMPANY.NAME.1"));

All<-Sep2013;
for (i in NAMES2[2:length(NAMES2)])
{j = get(i);
All<-merge(All,j,all=TRUE); 
# the default of by is to use the columns with common names between the two data frames.
}

# confirmed that after merging, the file has 48 columns.
ncol(All);

# check the weekday of each file is pulled.
table(wday(All$DATE.PULLED, label= TRUE));
# DATE.PULLED2 are month and year of each DATE.PULLED.
All$DATE.PULLED2<-as.yearmon(All$DATE.PULLED);

# EMP represents EXPIRATION.DATE-DATE.PULLED2 (in month).
All$EMP<-round((as.yearmon(All$EXPIRATION.DATE) - All$DATE.PULLED2)*12,digits = 0);
# The smallest number of EMP is -1, which means that once the member has passed
# the expiration date by one month, he/she is dropped out.
table(All$EMP);

# double chekc if All has any NA values.
dim(All[is.na(All$MEMBER.ID),]);
dim(All[is.na(All$MEMBER.SINCE.DATE),]);
dim(All[is.na(All$EXPIRATION.DATE),]);
dim(All[is.na(All$DATE.PULLED),]);
dim(All[is.na(All$DATE.PULLED2),]);
dim(All[is.na(All$STATUS),]);
dim(All[is.na(All$EMP),]);
```

## 6. What if the member renews the membership earlier than the current expiration date? 
* Does the expiration date get extended to one more year than the current expiration date? The answer is yes.
```{r RenewEarlier}
AllDate<-subset(All, select=c("MEMBER.ID","MEMBER.SINCE.DATE",
        "EXPIRATION.DATE","DATE.PULLED2","EMP"));

AllDate<-arrange(AllDate,MEMBER.ID,MEMBER.SINCE.DATE,EXPIRATION.DATE,
                 DATE.PULLED2);

# For every MEMBER.ID, extract the earliest DATE.PULLED2 for every
# EXPIRATION.DATE. This DATE.PULLED2 is the time when the member joined or
# renew their membership.

ID <- split(AllDate, AllDate$MEMBER.ID);
t<- do.call(rbind, lapply(ID, 
                function(x) (x[!duplicated(x$EXPIRATION.DATE),])));

# Some of the EMP are larger than 12.
# Check ID=638951, on 2014-01-31, the person renews the membership and the new expiration date
# is 2015-03-31, since the old expiration date is 2014-03-31. It confirms that
# if you renew your membership earlier than the current expiration date, your membership will
# be extended to one more year after your current expiration date.
# Same thing happened to ID=684951
t[t$MEMBER.ID=="638951",];
t[t$MEMBER.ID=="684951",];
```

## 7. Check how many times does each MEMBER.ID apprears in different DATE.PULLED2.
```{r Freq}
Freq <- AllDate[!duplicated(AllDate[c("MEMBER.ID","DATE.PULLED2")]),];
FreqID <-split(Freq, Freq$MEMBER.ID);

freq <- do.call(rbind, lapply(FreqID, 
                function(x) 
        data.frame(MEMBER.ID = unique(x$MEMBER.ID), 
                MEMBER.SINCE.DATE = min(x$MEMBER.SINCE.DATE),
                frequency = nrow(x))));
freq <- arrange(freq, MEMBER.SINCE.DATE);

freq <- cbind(freq, lable = 1:nrow(freq));
plot(freq[,4],freq[,3],xlab = "Member (ordered in MEMBER.SINCE.DATE)",
     ylab="Time appears in DATE.PULLED2")
```

## 8. Define Renew == 1.
* For the member who has EXPIRATION.DATE 4 months after the DATE.PULLED2, and renewed the membership within 10 months after DATE.PULLED2, label the member at DATE.PULLED2 with Renew == 1. If the member did not renew it within 10 months after DATE.PULLED2, then label Renew == 0.
```{r Renew}
        bgyr = "2013";
        bgmn = "12";
        endyr = "2016";
        endmn = "02";
        BG <- as.yearmon(as.Date(paste(bgyr,bgmn,"01", sep=""),"%Y%m%d"));
        END <- as.yearmon(as.Date(paste(endyr,endmn,"01", sep=""),"%Y%m%d"));

        dates <- as.yearmon(seq(from = as.Date(BG), 
                                to = as.Date(END), by = "month"));
        
        # Aug 2015 data is missing.
        dates <- dates[dates != "Aug 2015"];

        result <- All[FALSE,];

        for (i in 1:length(dates)) {
                test <- filter(All, DATE.PULLED2 == dates[i] & 
                                       as.yearmon(EXPIRATION.DATE) == dates[i] + 4/12);
                pullDate <- filter(All, (MEMBER.ID %in% test$MEMBER.ID) & 
                                           (DATE.PULLED2 > dates[i]) &
                                           (DATE.PULLED2 <= dates[i] + 10/12));
                renewID <- pullDate[as.yearmon(pullDate$EXPIRATION.DATE) 
                                    != (dates[i] + 4/12),]$MEMBER.ID;
                test$Renew <- 0;
                test[test$MEMBER.ID %in% renewID,]$Renew <- 1;
                result <- rbind(result, test);
                
        }

table(duplicated(result$MEMBER.ID));
which(duplicated(result$MEMBER.ID) == TRUE);
result[result$MEMBER.ID == "3125514",];
AllDate[AllDate$MEMBER.ID == "3125514",];

#result <- result[!duplicated(result$MEMBER.ID),];
dim(result[result$Renew == 1,]);

# write.xlsx(result,file="result.xlsx")
```



